---
title: "A good title to conceive"
author: "Author: Old Vegetable Bird"
date: "`r format(Sys.time(), '%F')`"
output:
    rmarkdown::html_document:
        theme: readable
        highlight: textmate
        df_print: paged
---

## Environment setup.

```{r message=F, warning=F}
rm(list = ls())
ptm <- proc.time()
# proc.time() - ptm
options(stringsAsFactors = F)
library("magrittr")
# library("stringr")
# library("dplyr")
# library("tidyr")
# library("tibble")
# library("purrr")
# library("readr")
# 
# library("fs")
# library("R.utils") # provide bzip2 function
```

# Initial commit using Git (for Windows)

```{r}
usethis::use_git()
file.remove(".git/hooks/pre-commit")
```

# Basic setting

```{r}
package_name <- "rTCRBCRr"

# available::available(package_name) # Check availability of the package name
```

# Make the hexagon sticker as the package logo

```{r}
library(ggplot2)
library(hexSticker)

dir.create("man/figures")

dir(system.file("man/figures", package = package_name))

image_path <- "man/figures/ggplot2_logo.png"

p <- ggplot(aes(x = Sepal.Width, y = Petal.Length), data = iris) + geom_point()
p <- p + theme_void() + theme_transparent()

sticker(p, package=package_name, p_size=20, s_x=1, s_y=.75, s_width=1.3, s_height=1,
        filename=image_path)

usethis::use_logo(image_path)
```

# Add the directory for package data preparation codes

```{r}
usethis::use_data_raw()
```


# Adds a CRAN package dependency to DESCRIPTION 

```{r}
usethis::use_package("magrittr")
usethis::use_package("tidyr")
usethis::use_package("tidyselect")
```

# Copy R scripts
# Copy inst/extdata files

```{r}
devtools::document()
```

# Render README rmarkdown file to README.md for github.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

```{r}
# usethis::use_readme_rmd() # Make README file via rmarkdown.
devtools::build_readme()
```

```{r}
usethis::use_mit_license()
```

```{r}
devtools::check()
```

```{r}
load_all()
```




```{r}
proc.time() - ptm
```


