---
title: "..."
author: "Author: ..."
date: "`r format(Sys.time(), '%F')`"
output:
    rmarkdown::html_document:
        theme: readable
        highlight: textmate
        df_print: paged
---

## Environment setup.

```{r message=F, warning=F}
rm(list = ls())
ptm <- proc.time()
# proc.time() - ptm
options(stringsAsFactors = F)
library("magrittr")
# library("stringr")
# library("dplyr")
# library("tidyr")
# library("tibble")
# library("purrr")
# library("readr")
# 
# library("fs")
# library("R.utils") # provide bzip2 function
```

https://mvuorre.github.io/exampleRPackage/

# Initial commit using Git (for Windows)

```{r}
usethis::use_git()
file.remove(".git/hooks/pre-commit")
```

# Basic setting

```{r}
package_name <- 'rTCRBCRr'

# available::available(package_name) # Check availability of the package name
```

# Make the hexagon sticker as the package logo

```{r}
library(ggplot2)
library(hexSticker)

dir.create("man/figures")

dir(system.file("man/figures", package = package_name))

image_path <- "man/figures/ggplot2_logo.png"

p <- ggplot(aes(x = Sepal.Width, y = Petal.Length), data = iris) + geom_point()
p <- p + theme_void() + theme_transparent()

sticker(p, package=package_name, p_size=20, s_x=1, s_y=.75, s_width=1.3, s_height=1,
        filename=image_path)

usethis::use_logo(image_path)
```

The helper use_r() creates and/or opens a script below R/. It really shines in a more mature package, when navigating between .R files and the associated test file.

```{r}
# usethis::use_r()
```


# Adds a CRAN package dependency to DESCRIPTION 

```{r}
usethis::use_package("magrittr")
usethis::use_package("tidyr")
usethis::use_package("tidyselect")
usethis::use_package("readr")
```

# Add the directory for package data preparation codes

```{r}
usethis::use_data_raw()
```

```{r}
devtools::load_all()
```

# prepare internal data for @examples tag of each exported function.

```{r}
present_tool <- c("trust", "mixcr")[1]
example_data_directory <- system.file(paste("extdata", present_tool, sep = "/"), package = "rTCRBCRr")
input_paths <- dir(example_data_directory, full.names = TRUE)
input_files <- dir(example_data_directory, full.names = FALSE)
input_files

sample_names <- sub(".tsv.*", "", input_files)
sample_names

raw_clonotype_dataframe_list <- lapply(input_paths, readr::read_tsv) %>%
    magrittr::set_names(., value = sample_names)
raw_clonotype_dataframe_list
```

# Prepare individual example data.

```{r}
raw_input_clonotype_dataframe <- raw_clonotype_dataframe_list[["sample_01"]]

immunarch_style_dataframe <- raw_input_clonotype_dataframe %>%
    format_clonotype_to_immunarch_style(., clonotyping_tool = present_tool)

nonproductive_CDR3aa_removed_dataframe <- immunarch_style_dataframe %>%
    remove_nonproductive_CDR3aa

chain_separated_dataframe <- nonproductive_CDR3aa_removed_dataframe %>%
    annotate_chain_name_and_isotype_name

convergent_clonotype_merged_dataframe <- chain_separated_dataframe %>%
    merge_convergent_clonotype

# input_dataframe <- nonproductive_CDR3aa_removed_dataframe
```

# Prepare a list of processed dataframes.

```{r}
the_divergent_clonotype_dataframe_list <- raw_clonotype_dataframe_list %>%
    lapply(., format_clonotype_to_immunarch_style, clonotyping_tool = present_tool) %>%
    lapply(., remove_nonproductive_CDR3aa) %>%
    lapply(., annotate_chain_name_and_isotype_name) %>%
    lapply(., merge_convergent_clonotype)
```


```{r}
# handle repertoire metrics for all the chains.
all_sample_all_chain_all_metrics_wide_format_dataframe_list <- the_divergent_clonotype_dataframe_list %>%
    lapply(., compute_repertoire_metrics_by_chain_name)

all_sample_all_chain_all_metrics_wide_format_dataframe_list

all_sample_all_chain_all_metrics_wide_format_dataframe <- all_sample_all_chain_all_metrics_wide_format_dataframe_list %>%
    combine_all_sample_repertoire_metrics

all_sample_all_chain_all_metrics_wide_format_dataframe

all_sample_all_chain_individual_metrics_dataframe_list <- all_sample_all_chain_all_metrics_wide_format_dataframe %>%
    get_item_name_x_sample_name_for_each_metric

all_sample_all_chain_individual_metrics_dataframe_list
```


```{r}
# handle repertoire metrics all all the isotypes of IGH chain.
all_sample_IGH_chain_all_metrics_wide_format_dataframe_list <- the_divergent_clonotype_dataframe_list %>%
    lapply(., calculate_IGH_isotype_proportion)

all_sample_IGH_chain_all_metrics_wide_format_dataframe_list

all_sample_IGH_chain_all_metrics_wide_format_dataframe <- all_sample_IGH_chain_all_metrics_wide_format_dataframe_list %>%
    combine_all_sample_repertoire_metrics

all_sample_IGH_chain_all_metrics_wide_format_dataframe

all_sample_IGH_chain_individual_metrics_dataframe_list <- all_sample_IGH_chain_all_metrics_wide_format_dataframe %>%
    get_item_name_x_sample_name_for_each_metric

all_sample_IGH_chain_individual_metrics_dataframe_list
```

# Save the object for examples used in function examples.

# Remember to manully add documentation in the /R/data.R file

```{r}
usethis::use_data(raw_input_clonotype_dataframe, overwrite = T)
usethis::use_data(immunarch_style_dataframe, overwrite = T)
usethis::use_data(nonproductive_CDR3aa_removed_dataframe, overwrite = T)
usethis::use_data(chain_separated_dataframe, overwrite = T)
usethis::use_data(convergent_clonotype_merged_dataframe, overwrite = T)

usethis::use_data(the_divergent_clonotype_dataframe_list, overwrite = T)

usethis::use_data(all_sample_all_chain_all_metrics_wide_format_dataframe_list, overwrite = T)
usethis::use_data(all_sample_all_chain_all_metrics_wide_format_dataframe, overwrite = T)
usethis::use_data(all_sample_all_chain_individual_metrics_dataframe_list, overwrite = T)
usethis::use_data(all_sample_IGH_chain_all_metrics_wide_format_dataframe_list, overwrite = T)
usethis::use_data(all_sample_IGH_chain_all_metrics_wide_format_dataframe, overwrite = T)
usethis::use_data(all_sample_IGH_chain_individual_metrics_dataframe_list, overwrite = T)
```

# The document for the package itself was created from the description file.

https://combine-australia.github.io/r-pkg-dev/other-documentation.html

```{r}
usethis::use_package_doc()
```

# Copy R scripts
# Copy inst/extdata files

```{r}
devtools::document()
```

# Render README rmarkdown file to README.md for github.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

```{r}
# usethis::use_readme_rmd() # Make README file via rmarkdown.
devtools::build_readme()
```

```{r}
# usethis::use_vignette("Quick_Start")
devtools::build_vignettes()
```




```{r}
usethis::use_mit_license()
```


# need to make custom change to make the workflow work.

```{r}
usethis::use_github_action("check-standard")
```


```{r}
devtools::check()
```

```{r}
devtools::install()
```


```{r}
devtools::build()
```


```{r}
proc.time() - ptm
```


