---
title: "Quick_Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick_Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of rTCRBCRr is to process the results from clonotyping tools such as trust, mixcr, and immunoseq to analyze the clonotype repertoire metrics

## Installation

You can **NOT** install the released version of rTCRBCRr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rTCRBCRr")
```

You can **ONLY** install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sciencepeak/rTCRBCRr")
```

## Example code

### Attach packages

```{r example}
library("rTCRBCRr")
library("magrittr")
library("readr")
```

### Read raw data files (trust generated for example) into a list of data frames

```{r message=FALSE, warning=FALSE}
input_paths <- dir(system.file("extdata", package = "rTCRBCRr"), full.names = TRUE)
input_files <- dir(system.file("extdata", package = "rTCRBCRr"), full.names = FALSE)
input_files

sample_names <- sub("_report.tsv.*", "", input_files)
sample_names

raw_clonotype_dataframe_list <- lapply(input_paths, readr::read_tsv) %>%
    magrittr::set_names(., value = sample_names)
raw_clonotype_dataframe_list
```

### Tidy up the clonotype dataframes

The tidy-up consists of four steps, namely four functions:

1. format_clonotype_to_immunarch_style
2. remove_nonproductive_CDR3aa
3. annotate_chain_name_and_cell_type 
4. merge_convergent_clonotype

#### Calculate and merge repertoire metrics for each sample in the list

This step consists of two functions.

1. compute_repertoire_metrics_by_chain_name
2. combine_all_sample_repertoire_metrics

```{r}
divergent_clonotype_dataframe_list <- raw_clonotype_dataframe_list %>%
    lapply(., format_clonotype_to_immunarch_style, clonotyping_tool = "trust") %>%
    lapply(., remove_nonproductive_CDR3aa) %>%
    lapply(., annotate_chain_name_and_cell_type) %>%
    lapply(., merge_convergent_clonotype)

all_sample_all_chain_all_metrics_wide_dataframe <- divergent_clonotype_dataframe_list %>%
    lapply(., compute_repertoire_metrics_by_chain_name) %>%
    combine_all_sample_repertoire_metrics

all_sample_all_chain_all_metrics_wide_dataframe
```

### Separate the all_sample_all_chain_all_metrics_wide_dataframe by individual metrics.

```{r}
individual_metrics_dataframe_list <- all_sample_all_chain_all_metrics_wide_dataframe %>%
    get_chain_name_x_sample_name_for_each_metric

individual_metrics_dataframe_list
```


## Clonotype repertoire metrics formulas

The repertoire metrics formula including richness, diversity (Shannon entropy), evenness (Pielou's eveness), and clonality were defined as follows, where $p_i$ is the frequency of ${\rm clonotype}_i$ in a sample with $N$ unique clonotypes ([Khunger, Rytlewski et al. 2019](https://doi.org/10.1080/2162402X.2019.1652538), [Looney, Topacio-Hall et al. 2020](https://doi.org/10.3389/fimmu.2019.02985)).

$$
richness\ =\ N
$$
$$
Shannon\ entropy=-\sum_{i=1}^{N}{p_i\log_2{\left(p_i\right)}}
$$
$$
Pielou\prime s\ eveness\ =\ \frac{Shannon\ entropy}{\log_2{N}}
$$
$$
clonality\ =\ 1\ -\ Pielou\prime s\ evenness
$$

The internal function `calculate_repertoire_metrics` is essential to implement the repertoire metrics formulas

```{r}
calculate_repertoire_metrics
```
